Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-08 methodology.tex
metion CODES validation against booksim in section 3.1, add cite for booksim
tweak methodology section based on Gail

We utilize the CODES simulation toolkit (Co-Design of Multilayer Exascale Storage Architectures)~\cite{codes}, which builds upon the ROSS parallel discrete event simulator~\cite{carothers_ross:_2002,barnes_warp_2013} to enable exploratory study of large scale systems of interest to the HPC community. CODES supports dragonfly~\cite{codes-dragonfly, misbah-tpds}, torus~\cite{misbah-pads-2014, ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with flit-level high-fidelity simulation. It can drive these models through an MPI simulation layer utilizing traces generated by the DUMPI MPI tracer~\cite{sst}.

@@

Two sets of parallel workloads are used in this study. Workload~\Rmnum{1} consists of AMG, MultiGrid and CrystalRouter. As shown in Table~\ref{tab:apps-detail}, AMG has the least amount of data transfer, making it the least communication-intensive job in the workload. Workload~\Rmnum{2} consists of sAMG, MultiGrid and CrystalRouter. sAMG, a synthetic version of AMG, is generated by increasing the data transferred in AMG's MPI calls by a factor of 100, making it the most communication-intensive job in the workload. We do this for reasons that will become clear in the following sections.

>>>>

We utilize the CODES simulation toolkit (Co-Design of Multilayer Exascale Storage Architectures)~\cite{codes}, which builds upon the ROSS parallel discrete event simulator~\cite{carothers_ross:_2002,barnes_warp_2013} to enable exploratory study of large scale systems of interest to the HPC community. CODES supports dragonfly~\cite{codes-dragonfly, misbah-tpds}, torus~\cite{misbah-pads-2014, ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with flit-level high-fidelity simulation. It can drive these models through an MPI simulation layer utilizing traces generated by the DUMPI MPI tracer~\cite{sst}. 
The behavior and performance of CODES dragonfly network model has been validated by Mishab et al.\ \cite{codes-dragonfly} against booksim, a serial cycle-accurate interconnection network simulator~\cite{booksim-simulator}.

@@

Two sets of parallel workloads are used in this study. Workload~\Rmnum{1} consists of AMG, MultiGrid and CrystalRouter. As shown in Table~\ref{tab:apps-detail}, AMG has the least amount of data transfer, making it the least communication-intensive job in the workload. Workload~\Rmnum{2} consists of sAMG, MultiGrid and CrystalRouter. sAMG, a synthetic version of AMG, is generated by increasing the data transferred in AMG's MPI calls by a factor of 100, making it the most communication-intensive job in the workload. We add sAMG for reasons that will become clear in the following sections.
